wgcna

### 2019-09-03 analysis/08_wgcna.Rmd
only looking at pituitary

## Females

```{r wgcna-female, message=FALSE, warning=FALSE, cache=TRUE}
subsetWGCNA(whichgroups = c("female.gonad", "female.hypothalamus", "female.pituitary"),
            mytitle = "Female sample dendrogram with trait heatmap")

**Fig 2. Female characterization dendrogram with trait heatmap.**. 
Most pituitary samples form a single cluster. More hypothalamus samples cluster with gonads than with pituitary.

## Males

```{r wgcna-male, message=FALSE, warning=FALSE, cache=TRUE}
subsetWGCNA(c("male.gonad", "male.hypothalamus", "male.pituitary"),
            mytitle = "Male sample dendrogram with trait heatmap")

**Fig 3. Male characterization dendrogram with trait heatmap.**. 
 As with females, most pituitary samples form a single cluster, while more hypothalamus samples cluster with gonads than with pituitary.

## gonads

```{r wgcna-gon, message=FALSE, warning=FALSE, cache=TRUE}
subsetWGCNA(c("female.gonad", "male.gonad"),
            mytitle = "Gonad dendrogram with trait heatmap")
```

**Fig 3. Gonad characterization dendrogram with trait heatmap.**. 
Male and female samples cluster together, but with large, sex-specific regions.... maybe there is a strong treatment effect here.

## hypothalamus

```{r wgcna-hyp, message=FALSE, warning=FALSE, cache=TRUE}
subsetWGCNA(c("male.hypothalamus", "female.hypothalamus"),
            mytitle = "Hypothalamus dendrogram with trait heatmap")
```

Male and female samples cluster together, but with very small, sex-specific regions.... maybe there is a small treatment effect here.

@@

#subsetWGCNA(c("female.pitutary", "male.pitutary"),
#            mytitle = "Pituitary dendrogram with trait heatmap")
```

## female hypothalamus

```{r wgcna-f-hyp, message=FALSE, warning=FALSE, cache=TRUE}
subsetWGCNA(c("female.hypothalamus"),
            mytitle = "Female hypothalamus sample dendrogram")
```

## female gonad

```{r wgcna-f-gon, message=FALSE, warning=FALSE, cache=TRUE}
subsetWGCNA(c("female.gonad"),
            mytitle = "Female gonad sample dendrogram")
```

>>>>

@@

subsetWGCNA(c("female.pitutary", "male.pitutary"),
            mytitle = "Pituitary dendrogram with trait heatmap")
```
